### 2024-03-11 thesis/chapters/04-implementation.tex
Change two time domain features and reevaluate

\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us. It serves as a test bed during the sensor unit development. The sensor is placed on the plastic casing at the back of the drive motor. The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}). It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm). Acceleration observed is $\pm 5\;\mathrm{m/s}^2$ in radial and tangential directions, and $\pm 1\;\mathrm{m/s}^2$ in axial direction.

\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}). Altogether, two units are available in two independent air conditioning units for the data center. The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz). Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll. Accelerations picked up by the sensor are $\pm 3\;\mathrm{m/s}^2$ tops.

@@

The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}). The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz). The electric motor provides 400~kW of power (class~\rom{3}). The outer bearing on the pump vibrates with an acceleration of $\pm 5 \;\mathrm{m/s}^2$.

@@

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
\textbf{Bus}                                     & Analog           & SPI                \\ \hline
\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 to 16      \\ \hline
\textbf{Bandwidth} (kHz)                         & 0.55 - 1.6       & 5 - 6.3            \\ \hline
\textbf{Sensitivity} (mg/LSB)                    & 2.930            & 0.061       \\ \hline
\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
\end{tabular}
\caption{Hardware parameters of previous and proposed sensor units}
\label{tab:design:hw-sensors}
\end{table}

@@

\section{Preliminary measurements}
During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals. Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}. The acceleration rarely exceeds 1~g.

In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz). The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
        \caption{Acceleration in $\mathrm{m/s}^2$}
        \label{fig:design:preliminary-acceleration}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.49\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
        \caption{Approximate velocity in $\mathrm{mm/s}$}
        \label{fig:design:preliminary-velocity}
    \end{subfigure} 
    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
\end{figure}

Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule. The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks. Envelopes must be tweaked further to achieve more accurate values. The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.

\begin{figure}[h]
    \centering
    \begin{subfigure}[b]{0.45\textwidth}
        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
		\caption{Orbital analysis of compressor's \nth{1}~harmonic frequency}
		\label{fig:design:orbital-analysis}
    \end{subfigure}
    \hfill
    \begin{subfigure}[b]{0.54\textwidth}
        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
        \caption{FFT with Hann window of length $2^{10}$ ($\approx$~409~ms)}
        \label{fig:design:preliminary-spectrum}
    \end{subfigure} 
    \caption{Orbital and spectral methods of vibration signal analysis}
\end{figure}

>>>>

\textbf{Standing fan} is model \emph{Kalorik~TKG~VT1037} (Fig.~\ref{fig:machine:fan}) and one unit is available to us. It serves as a test bed during the sensor unit development. The sensor is placed on the plastic casing at the back of the drive motor. The fan has a 45~cm diameter with 3~propellers and a power of 45~W (class~\rom{1}). It has a switch for 3 rotational speeds, which are approximately 18.5~Hz (1100~rpm), 20.4~Hz (1200~rpm), and 22~Hz (1300~rpm).

\textbf{Scroll compressor} is model \emph{Copeland~ZR16} (Fig.~\ref{fig:machine:compressor}). Altogether, two units are available in two independent air conditioning units for the data center. The compressor has 9.7~kW of power (class~\rom{1}) and rotates at 2900 rpm (48.3 Hz). Two possible measurement locations are located on the sides on top of the bearings, just above the base and above the scroll.

@@

The newer primary pumps with bundled wireless cloud monitoring system are two units of \emph{KSB Omega~300-560} (Fig.~\ref{fig:machine:pump-ksb}). The pumps were commissioned in 2018, and they rotate at 1493 rpm (24.9 Hz). The electric motor provides 400~kW of power (class~\rom{3}).

@@

\begin{table}[ht]
\renewcommand{\arraystretch}{1.2}
\centering
\begin{tabular}{|l|l|l|}
\hline
\textbf{Accelerometer}                           & \textbf{ADXL335} & \textbf{IIS3DWB}   \\ \hline
\textbf{Vendor}                                  & Analog Devices   & STMicroelectronics \\ \hline
\textbf{Bus}                                     & Analog           & SPI                \\ \hline
\textbf{Axis}                                    & 3                & 1 or 3             \\ \hline
\textbf{Range} (g)                               & $\pm$ 3          & $\pm$ 2 - 16      \\ \hline
\textbf{Bandwidth} (kHz)                         & 0.55 - 1.6       & 5 - 6.3            \\ \hline
\textbf{Sensitivity} (mg/LSB)                    & 2.93            & 0.06 - 0.49       \\ \hline
\textbf{Noise density} ($\mu g / \sqrt{\mathrm{Hz}}$ rms) & 150 - 300        & 75                 \\ \hline
\textbf{Microcontroller}                         & Beaglebone Black & ESP32-PoE-ISO      \\ \hline
\textbf{CPU SoC}                                 & TI Sitara AM3358 & ESP32-WROOM-32     \\ \hline
\textbf{Output data rate} (kHz)                  & 2.5              & 26.7               \\ \hline
\textbf{ADC resolution} (bit)                    & 12               & 16                 \\ \hline
\textbf{FIFO}                                    & -                & 3 kB (512 samples) \\ \hline
\end{tabular}
\caption{Hardware parameters of previous and proposed sensor units}
\label{tab:design:hw-sensors}
\end{table}

@@

\section{Firmware}
% Timing is crutial 19ms.
Activity diagrams describe three basic actions of firmware for logging accelerometer samples:

\begin{itemize}
\itemsep0pt
\item begin new recording, 
\item log block of samples into CSV file,
\item finish recording.
\end{itemize}

\begin{figure}[h]
    \centering
	\includegraphics[width=\textwidth]{assets/design/firmware-design.png}
\end{figure}

\section{Dataset description}

\section{BVS cloud}

\section{Compressors}

\section{Water pumps}

%\section{Preliminary measurements}
%During the initial on-site inspections of machinery, we carried out preliminary measurements of vibration signals. Raw waveforms of acceleration for the fan, two different compressors, and the outer bearing on a pump and motor in three axes are plotted in Figure~\ref{fig:design:preliminary-acceleration}. The acceleration rarely exceeds 1~g. 
%
%In frequency spectra in Figure~\ref{fig:design:preliminary-spectrum} behavior of machines can be clearly discerned below the resonance frequency of the accelerometer (550 Hz). The compressor suspected to be faulty has a stronger \nth{4} harmonic and above than the other one.
%
%
%\begin{figure}[h]
%    \centering
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-temporal.png}
%        \caption{Acceleration in $\mathrm{m/s}^2$}
%        \label{fig:design:preliminary-acceleration}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.49\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-velocity.png}
%        \caption{Approximate velocity in $\mathrm{mm/s}$}
%        \label{fig:design:preliminary-velocity}
%    \end{subfigure} 
%    \caption{Temporal domain waveforms in all spatial directions with 300 ms duration at 1 s timestamp}
%\end{figure} 
%
%Figure~\ref{fig:design:preliminary-velocity} documents the effort to obtain vibration velocity (as per ISO~20186) by integration with the composite trapezoidal rule. The significant drift after integration is eliminated by subtracting the mean of the envelope constructed using cubic interpolation of peaks. Envelopes must be tweaked further to achieve more accurate values. The orbital plot of the first harmonic frequency $f_{max} \pm 5\;\mathrm{Hz}$ in Figure~\ref{fig:design:orbital-analysis} allows us to check the sensor deviation out of the axis of rotation.
%
%\begin{figure}[h]
%    \centering
%    \begin{subfigure}[b]{0.45\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/compressor-orbitals-1x.png}
%		\caption{Orbital analysis of compressor's \nth{1}~harmonic frequency}
%		\label{fig:design:orbital-analysis}
%    \end{subfigure}
%    \hfill
%    \begin{subfigure}[b]{0.54\textwidth}
%        \includegraphics[width=\textwidth]{assets/design/EDA-custom-dataset-spectral-X-axis.png}
%        \caption{FFT with Hann window of length $2^{10}$ ($\approx$~409~ms)}
%        \label{fig:design:preliminary-spectrum}
%    \end{subfigure} 
%    \caption{Orbital and spectral methods of vibration signal analysis}
%\end{figure}

### 2024-03-11 thesis/chapters/appendix/A-resume.tex
BVS cloud analysis for last year
Change two time domain features and reevaluate

Symptómy porúch rotačných strojov sa prejavujú rôznymi frekvenčnými pásmami, ale väčšina je závislá od rotačnej rýchlosti súčiastky. Nevyváženosť, nevyváženosť a vôľa sa bežne objavujú v frekvenciách do 300 Hz. Poruchy ložísk a prevodovky v neskorých štádiách vývoja sa prejavujú v rozsahu medzi 300 Hz a 1 kHz. Vyššie frekvencie do 10 kHz pomáhajú odhaliť poruchy ložísk v skorších štádiách rozvoja.

@@

Presná viactriedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií. Algoritmus k-najbližších susedov (KNN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti. Nachádza uplatnenie aj v učení čiastočne s učiteľom, pretože dokáže odvodiť označenia len zo znalosti niekoľkých anotácií.

@@

Tri typy experimentov s modelom KNN prebiehajú s validáciou metódou hold-out, Najprv sa model naučí všetky extrahované prvky, takže nedochádza k výberu prvkov. Metódou hrubej sily sa hľadá kombinácia troch atribútov s najvyššou trénovaciou presnosťou. Následne sa porovnáva presnosť modelu pre tri atribúty zvolené technikami výberu atribútov. Dávkový model KNN slúži ako referenčný, podľa ktorého sa posudzuje KNN v postupnom učení.

Online učenie napodobňuje sťažené podmienky diagnostiky strojov, ktoré sa objavujú v praxi. Oneskorené dodanie alebo vynechanie skutočných značiek nepochybne znižuje spoľahlivosť klasifikácie. Modely KNN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A nad všetkými extrahovanými atribútmi. Týmto spôsobom môžeme porovnať trénovacie presnosti tréningu pre dávkové a postupné učenie. KNN sme nastavili na 5 susedov a euklidovskú vzdialenosť. Metriky online učenia sa vyhodnocujú v metódou progresívnom vyhodnocovanie na ešte nevyváženom súbore údajov.

@@

Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov. Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť KNN modelu oproti metrikám samostatne. Žiadny prístup však nedokázal nájsť trojicu prediktorov s presnosťou blízkou optimálnej, ktorá je až 98\%. Trénovanie KNN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.

Model postupného učenia kNN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov. Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.  Doteraz boli urobené závery podľa súboru údajov MaFaulDa, ktoré plánujeme overiť na súbore údajov získaných v priemysle počas DP3.

>>>>

Symptómy porúch rotačných strojov sa prejavujú rôznymi frekvenčnými pásmami, ale väčšina je závislá od rotačnej rýchlosti súčiastky. Nevyváženosť, nesúosovosť a vôľa sa bežne objavujú v frekvenciách do 300 Hz. Poruchy ložísk a prevodovky v neskorých štádiách vývoja sa prejavujú v rozsahu medzi 300 Hz a 1 kHz. Vyššie frekvencie do 10 kHz pomáhajú odhaliť poruchy ložísk v skorších štádiách rozvoja.

@@

Presná viactriedna klasifikácia príčin porúch stroja podľa vopred známych charakteristík je oveľa náročnejšia úloha ako objavenie anomálií. Algoritmus k-najbližších susedov (k-NN) priradí pozorovanie triede, do ktorej patrí väčšina $k$ bodov v blízkom okolí podľa použitej miery vzdialenosti. Nachádza uplatnenie aj v učení čiastočne s učiteľom, pretože dokáže odvodiť označenia len zo znalosti niekoľkých anotácií.

@@

Tri typy experimentov s modelom k-NN prebiehajú s validáciou metódou hold-out, Najprv sa model naučí všetky extrahované prvky, takže nedochádza k výberu prvkov. Metódou hrubej sily sa hľadá kombinácia troch atribútov s najvyššou trénovaciou presnosťou. Následne sa porovnáva presnosť modelu pre tri atribúty zvolené technikami výberu atribútov. Dávkový model k-NN slúži ako referenčný, podľa ktorého sa posudzuje k-NN v postupnom učení.

Online učenie napodobňuje sťažené podmienky diagnostiky strojov, ktoré sa objavujú v praxi. Oneskorené dodanie alebo vynechanie skutočných značiek nepochybne znižuje spoľahlivosť klasifikácie. Modely k-NN v experimentoch s postupným učením sú trénované na rovnakom základnom súbore údajov pre ložisko A nad všetkými extrahovanými atribútmi. Týmto spôsobom môžeme porovnať trénovacie presnosti tréningu pre dávkové a postupné učenie. k-NN sme nastavili na 5 susedov a euklidovskú vzdialenosť. Metriky online učenia sa vyhodnocujú v metódou progresívnom vyhodnocovanie na ešte nevyváženom súbore údajov.

@@

Dosiahnuté stratové kompresné pomery pre MaFaulDa sú 2381:1 pre všetky atribúty a 25000:1 pre šesť atribútov. Výber atribútov metódou súčinu poradí zabezpečí väčšinou najlepšiu presnosť k-NN modelu oproti metrikám samostatne. Žiadny prístup však nedokázal nájsť trojicu prediktorov s presnosťou blízkou optimálnej, ktorá je až 98\%. Trénovanie k-NN na troch hlavných komponentoch prinieslo lepšiu presnosť ako výber atribútov.

Model postupného učenia k-NN dosahuje prinajlepšom 90\% presnosť s okamžitou spätnou väzbou, 85\% so značkami oneskorenými o 250 pozorovaní a 82\% s iba 25\% anotovaného súboru údajov. Porovnateľný model trénovaný v dávkach dosahuje presnosť 98\%.  Doteraz boli urobené závery podľa súboru údajov MaFaulDa, ktoré plánujeme overiť na súbore údajov získaných v priemysle počas DP3.

### 2024-03-11 thesis/chapters/appendix/B-plan-of-work.tex
Change two time domain features and reevaluate

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
\\ \hline
\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
 \\ \hline
\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
 \\ \hline
\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
 \\ \hline
\nth{6} week         & Feature selection used in KNN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore incremental learning KNN algorithm with MaFaulDa dataset. Consultation and status report.
 \\ \hline
 \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
 \\ \hline
 \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for kNN validation. Consultation to discuss progress.
 \\ \hline
  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning. Fix the sampling rate issue in the provisional sensor unit.
 \\ \hline
  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump.
 \\ \hline
  \nth{12} - \nth{15} week         &  Write up design chapter: research questions, visualization export. Finish writing chapter on design and implementation.
 \\ \hline
\end{tabular}
\end{table}

@@

\section{Summer semester - DP3}
\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1}  - \nth{2} week         & 
\begin{enumerate}
\itemsep0pt
\item Incorporate suggestions from DP2 defense. 
\item Develop and test firmware for designed sensor unit.
\end{enumerate}
\\ \hline
\nth{2}  - \nth{10} week         & 
\begin{enumerate}
\itemsep0pt
\item Long-term manual regular gathering of vibration data from compressors and pumps. 
\item Find optimal number of features. 
\item Try to increase KNN prediction metrics.
\item Put together incremental learning with feature selection. 
\item Explore incremental clustering in search of method that can help with labeling.
\end{enumerate}
\\ \hline
\nth{10} - \nth{12} week         & Conclude results from measurements in real environment.
 \\ \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1} week         & Semester kickoff meeting to set goals, and experiments and discuss the status of collaborations with partners.
\\ \hline
\nth{2} week         &  Arrange collaboration with an alternative industry partner. Prepare a checklist for the technical inspection of machinery. Construct a device for exploratory measurements.
\\ \hline
\nth{3} week         & Technical inspection of air conditioning units in the data center. Feature extraction step to calculate features from MaFaulDa.
 \\ \hline
\nth{4} week         & Consultation about plan for machine to measure in the data center and better device for measurement.
 \\ \hline
\nth{5} week         &  In feature selection using various metrics to determine sets of best features in the MaFaulDa.
 \\ \hline
\nth{6} week         & Feature selection used in k-NN multiclass and binary classificator.
 \\ \hline
\nth{7} week         & Explore incremental learning k-NN algorithm with MaFaulDa dataset. Consultation and status report.
 \\ \hline
 \nth{8} week         & Shorten analysis chapter about wavelets. Look at clustering detection incremental learning in MaFaulDa.
 \\ \hline
 \nth{9} week         &  Refactor separate trials in feature selection to integrate them into the pipeline for k-NN validation. Consultation to discuss progress.
 \\ \hline
  \nth{10} week         & Include incremental learning in analysis. Experiment with gradual feature selection in incremental learning. Fix the sampling rate issue in the provisional sensor unit.
 \\ \hline
  \nth{11} week         & Consultation in preparation for machine inspections. Preliminary measurements of fan, compressors, and pump.
 \\ \hline
  \nth{12} - \nth{15} week         &  Write up design chapter: research questions, visualization export. Finish writing chapter on design and implementation.
 \\ \hline
\end{tabular}
\end{table}

@@

\section{Summer semester - DP3}
\begin{table}[h!]
\def\arraystretch{1.25}
\begin{tabular}{|l|p{12cm}|}
\hline
\textbf{Period} & \textbf{Work}                                                                                                                                                                                                                         \\ \hline
\nth{1}  - \nth{2} week         & 
\begin{enumerate}
\itemsep0pt
\item Incorporate suggestions from DP2 defense. 
\item Develop and test firmware for designed sensor unit.
\end{enumerate}
\\ \hline
\nth{2}  - \nth{10} week         & 
\begin{enumerate}
\itemsep0pt
\item Long-term manual regular gathering of vibration data from compressors and pumps. 
\item Find optimal number of features. 
\item Try to increase k-NN prediction metrics.
\item Put together incremental learning with feature selection. 
\item Explore incremental clustering in search of method that can help with labeling.
\end{enumerate}
\\ \hline
\nth{10} - \nth{12} week         & Conclude results from measurements in real environment.
 \\ \hline
\end{tabular}
\end{table}

### 2024-03-11 thesis/chapters/preliminaries/annotation.tex
Change two time domain features and reevaluate

The progress report in Master's thesis project \rom{2} deals with condition monitoring and predictive maintenance of rotating machinery by employing feature discovery and statistical classification.

@@

Priebežná správa o riešení DP2 sa zaoberá monitorovaním stavu rotačných strojov a ich prediktívnou údržbou prostredníctvom techník výberu atribútov a štatistickej klasifikácie.

>>>>

Master's thesis deals with condition monitoring and predictive maintenance of rotating machinery by employing feature discovery and statistical classification.

@@

Diplomová práca sa zaoberá monitorovaním stavu rotačných strojov a ich prediktívnou údržbou prostredníctvom techník výberu atribútov a štatistickej klasifikácie.
